Cartogram Mapping and its Application to Cancer Data Visualization

### 2019-09-24 review_article.Rmd
cannot fit tilegrid on single page

As the trade-off regarding boundaries approaches simplicity, the distortion of region shapes on the contiguous cartogram presents an additional hurdle to visual recognition and this hurdle is not only eliminated on the non-contiguous cartogram but is replaced by the meaningful empty-space property [@NAC, @ECGC].
The shapes are valuable for recognition and allows users to orient themselves on the display. Map creators can efficiently communicate with this kind of map by keeping the outlines or particular elements of the original in the new shape [@NISCC].
The scale of the areas does not impact on the shape recognition.
However it may impact on the visibility of all areas if small areas expand beyond their boundaries. 
Figure \ref{fig:ggcartograms} b shows small overlaps in the north east region of the United States. These overlaps are also shown in the non-contiguous cartogram of Australia in Figure \ref{fig:auscartograms} b.

@@

```{r ggtilemap, fig.cap = "A tile map and geofaceted map of the Unites States of America. Each state in the tile map has been colored according to the average age-adjusted rate of incidence for lung and bronchus for females and males in the United States 2012-2016. Each state has been represented by a square, each square is the same size. The geofaceted map allows the rates for males and females to be contrasted. It has the same layout as the tile map, but shows more information per state than ", message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width = "100%"}
knitr::include_graphics("figures/gggrids.png")
```

>>>>

As the trade-off regarding boundaries approaches simplicity, the distortion of region shapes on the contiguous cartogram presents an additional hurdle to visual recognition and this hurdle is not only eliminated on the non-contiguous cartogram but is replaced by the meaningful empty-space property [@ECGC, @NAC].
The shapes are valuable for recognition and allows users to orient themselves on the display. Map creators can efficiently communicate with this kind of map by keeping the outlines or particular elements of the original in the new shape [@NISCC].
The scale of the areas does not impact on the shape recognition.
However it may impact on the visibility of all areas if small areas expand beyond their boundaries. 
Figure \ref{fig:ggcartograms} b shows small overlaps in the north east region of the United States. These overlaps are also shown in the non-contiguous cartogram of Australia in Figure \ref{fig:auscartograms} b.

@@

```{r ggtilemap, fig.cap = "A tile map and geofaceted map of the Unites States of America. Each state in the tile map has been colored according to the average age-adjusted rate of incidence for lung and bronchus for females and males in the United States 2012-2016. Each state has been represented by a square, each square is the same size. The geofaceted map allows the rates for males and females to be contrasted. It has the same layout as the tile map, but shows more information per state.",fig.height = 8, fig.width = 5}
knitr::include_graphics("figures/gggrids.png")
```
